---
title: "Data in a day"
output: html_notebook
---

## Import libraries
```{r}
library("jsonlite")
library("plyr")
```

## Source the data
Use the firebase API to pull ball dropping data
```{r}
json_data <- fromJSON("https://newton-decoded.firebaseio.com/falls.json")
```


## Explore and transform the data

Let's have a look at what comes back from the API - it doesn't look very friendly to work with.
```{r}
print(json_data)
```

We need to create a function to help us make rows of data from our json
```{r}
createRow <- function(balldrop){
 data.frame("height"=balldrop$x,"time2"=balldrop$y)
}
```

Using Hadley's plyr library we can go through the whole json and put all the rows of data together
```{r}
df <- ldply(json_data, createRow)
```

Let's have a look at it now - much better!
```{r}
head(df)
```

```{r}
summary(df)
```

Visualise the data
```{r}
# write code here to plot data - use tab to help you
```


## Building a model
Build a linear mathematical model - this is using calculus under the hood to find the best line.
```{r}
linearModel <- lm(time2 ~ . , data=df)
```

## Evaluate your model
The first thing to do is eyeball it to get a feel for what we have built.
```{r}
# write code here to plot data - use tab to help you
abline(linearModel)
```

We can also be quantitative with evaluation of our predictions by looking at the error between our predictions and our model - using the R-Squared value, 1 is perfect, 0 is terrible.
```{r}
summary(linearModel)$r.squared
```
